\section{Introduction}

Steganography and cryptography solve different problems. Cryptography protects semantic content, but it can still expose that protected communication is taking place. Steganography targets a stronger operational objective in many censorship settings: make communication appear ordinary enough that transmission itself does not stand out. In text channels this objective is difficult because linguistic artifacts can be exposed by either human inspection or algorithmic detection.

Generation-based linguistic steganography has become practical only after modern language models reached useful fluency and contextual consistency. Neural Linguistic Steganography (NLS)~\cite{ziegler2019neural} established a key baseline by combining arithmetic coding with neural next-token distributions, showing that distribution-preserving design can coexist with useful payload capacity. OD-Stega~\cite{huang2026odstega} extended that line with explicit constrained optimization and detailed discussion of implementation friction points, especially tokenization mismatch and finite-runtime tradeoffs. These two papers form the mandatory conceptual anchors for our draft.

This paper presents \textbf{Ghostext}, a system-oriented implementation that follows the arithmetic-coding generation path while emphasizing deterministic synchronization, authenticated packet handling, and fail-closed decoding semantics. The core three-role narrative is unchanged from the standard formulation. Alice starts from a prompt, a passphrase, and a secret message. Ghostext encrypts the message, maps encrypted bits into token choices through interval narrowing, and emits fluent cover text. Bob, with the same protocol-sensitive configuration, inverts token choices back to packet bytes and decrypts. A passive censor observes only the transmitted text.

The working title and target narrative are intentionally explicit: \emph{Ghostext: an almost perfect stenography via large language model and arithmetic coding}. In this draft, ``almost perfect'' is neither a theorem claim nor marketing language. It is a constrained design intention under finite precision and finite-length generation: preserve model-driven token behavior as much as practical while using near-available embedding entropy, and explicitly fail when synchronization assumptions break.

\paragraph{Why an evidence-first draft now.}
The current repository state is under an explicit experiment pause. That pause is useful for writing discipline: it forces us to separate what the implementation already guarantees from what still needs controlled measurement. Therefore this manuscript does not present new detector-resistance benchmarks or active-channel robustness experiments. Instead, it contributes an implementation-backed protocol description, a strict claim boundary framework, and a reproducibility-first evaluation plan for post-pause execution.

\paragraph{Main contributions of this draft.}
This version makes four contributions to the CCS writing process. First, it gives a protocol-level description aligned with concrete code behavior in \texttt{../Ghostext}, including packet encryption, key separation, synchronization fingerprinting, and interval codec operation. Second, it introduces explicit claim discipline that labels statements as implemented facts, inferences, or future work. Third, it documents reliability-oriented system design choices such as deterministic quantization, retokenization-stability filtering, and fail-closed decode checks. Fourth, it defines a post-pause measurement protocol centered on recoverability, runtime cost, and reproducibility before broader detector-facing claims.

\paragraph{Scope and non-scope in one sentence.}
Ghostext currently aims to be a reliable, reproducible, passive-censor steganography system; strong active-adversary robustness and detector-evasion generalization remain planned work.
