\section{Problem Setting and Threat Model}
\subsection{Communication Goal}
Two parties (sender and receiver) share secret material and protocol-sensitive runtime configuration. The sender transforms a plaintext message into an encrypted packet and embeds it into generated text. The receiver observes the text and attempts to recover the original plaintext.

We distinguish two outcomes:
\begin{itemize}
\item \textbf{Matched configuration:} successful plaintext recovery.
\item \textbf{Mismatched configuration/channel:} explicit decoding failure (fail-closed), rather than silent approximate output.
\end{itemize}

\subsection{Adversary Model}
Our baseline adversary is a \emph{passive observer}:
\begin{itemize}
\item can read the transmitted cover text,
\item does not know sender/receiver secret material,
\item does not actively edit, reorder, or truncate the token sequence in transit.
\end{itemize}

This model follows a pragmatic first-step security scope for covert communication engineering: correctness and explicit boundary behavior under passive observation.

\subsection{System Assumptions}
Ghostext requires strict synchronization between sender and receiver for all protocol-sensitive factors, including:
\begin{itemize}
\item model/backend identity and tokenizer behavior,
\item prompt and prompt-template behavior,
\item seed and runtime generation controls relevant to distribution reconstruction,
\item candidate policy, quantization policy, and interval codec settings.
\end{itemize}

If these assumptions are violated, Ghostext is designed to fail explicitly.

\subsection{Non-Goals in This Version}
The current system does not claim:
\begin{itemize}
\item robustness to active text modifications (insert/delete/replace/rewrite),
\item guaranteed resistance against dedicated steganalysis models,
\item interoperability across model families or version drift.
\end{itemize}

\subsection{Security Objectives}
Within the stated model and assumptions, Ghostext targets:
\begin{itemize}
\item \textbf{Recoverability:} deterministic decode under matched conditions.
\item \textbf{Fail-closed behavior:} explicit failure under mismatch, instead of ambiguous outputs.
\item \textbf{Reproducibility:} rerunnable behavior and auditable configuration coupling.
\end{itemize}
