\section{Threat Model}

\subsection{Roles and Shared State}

Ghostext has three roles: Alice (sender), Bob (receiver), and Censor (observer). Alice and Bob share passphrase and protocol-sensitive configuration. Shared configuration includes model/tokenizer identity, prompt, seed, candidate policy, quantization settings, and codec/crypto parameters.

\subsection{Primary Adversary}

The primary adversary is a passive Censor that observes text but does not modify transport content. The Censor does not know the passphrase. Prompt knowledge is treated as an adversarial capability axis: we report our baseline analysis under unknown-prompt assumption and explicitly discuss risks when prompt templates are predictable.

\subsection{Additional Realistic Attack Surfaces}

Beyond pure text inspection, we consider three practical surfaces that require explicit measurement beyond the current baseline.

\textbf{Multi-message accumulation}: detector sees many samples from one sender.

\textbf{Traffic side channels}: detector observes length/timing distributions.

\textbf{Model-family fingerprinting}: detector compares outputs against likely model/prompt families.

Ghostext currently provides defensive engineering hooks for these surfaces (failure taxonomy, retry controls, and configuration binding), but does not yet claim empirical robustness against them.

\subsection{Capability Matrix}

For clarity, Table~\ref{tab:threat-capabilities} summarizes which adversary capabilities are in scope for implemented defenses and which are either covered in baseline measurements or kept as pending measured dimensions.

\begin{table}[t]
\caption{Threat-capability matrix for current Ghostext scope.}
\label{tab:threat-capabilities}
\begin{tabular}{p{0.40\linewidth}p{0.21\linewidth}p{0.31\linewidth}}
\toprule
Adversary capability & Scope status & Current handling \\
\midrule
Passive text observation & in scope & deterministic protocol + fail-closed checks \\
Prompt-template knowledge & measured axis & separate unknown/template-known regimes in evaluation plan \\
Multi-message accumulation & measured axis & explicit detector-aggregation block in staged protocol \\
Traffic timing/length observation & measured axis & retry and latency/length logging with baseline summaries and pending condition expansion \\
Active text modification in transit & out of scope (current version) & no robustness claim; reserved for future extension \\
Runtime compromise of sender/receiver endpoint & out of scope (current version) & no claim; orthogonal endpoint-security problem \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Assumption Boundaries}

Two assumptions deserve explicit caveats. First, sender and receiver need synchronized runtime state, including tokenizer-compatible behavior. Configuration fingerprinting detects drift but does not remove the operational need for configuration hygiene. Second, passphrase secrecy is required for packet confidentiality and integrity; if endpoint secrets are compromised, steganographic concealment alone is insufficient.

These boundaries are not unique to Ghostext, but making them explicit is important for conservative claim wording.

\subsection{Security Objective in This Paper}

The objective of this paper is modest and explicit: provide a deterministic, fail-closed, implementation-auditable steganographic protocol with bounded approximation analysis and a reproducible evaluation framework. Strong detector-evasion claims remain pending until dedicated detector and traffic-side stages are completed.
