\section{Design Overview}
Ghostext is an encrypt-then-steganography pipeline over next-token distributions. Alice first transforms plaintext into an authenticated encrypted packet. Ghostext then maps packet bits to token choices by finite-interval coding constrained by model probabilities. Bob mirrors the same process in reverse. The system is built for deterministic synchronized decoding, not for approximate decoding under drift.

Our design balances four goals. The first goal is confidentiality and integrity before embedding: payload semantics are protected cryptographically before any token-level mapping begins. The second goal is deterministic recoverability under matched configuration. The third goal is explicit fail-closed behavior under mismatch. The fourth goal is reproducibility through explicit, auditable configuration surfaces.

Concretely, Ghostext has six components. The packet/crypto component constructs an opaque bootstrap and encrypted body. The backend component provides tokenization, rendering, and next-token distributions. The candidate policy component applies top-$p$, max-candidate, and entropy gates, then enforces retokenization stability when enabled. The quantization component turns floating probabilities into deterministic integer frequencies and CDF ranges. The interval codec component performs encoding and decoding over finite integer intervals. Finally, the pipeline orchestrates header/body segmentation, token budgets, retries, and error propagation.

The key synchronization mechanism is configuration fingerprinting. Ghostext hashes protocol-relevant runtime configuration, backend metadata, and prompt hash into a compact fingerprint and binds it to encrypted header metadata. This coupling prevents silent decode drift from being interpreted as a successful decryption.
