\section{System Overview and Operational Semantics}

\begin{figure*}[t]
\centering
\begin{tikzpicture}[
    node distance=6mm and 6mm,
    stage/.style={draw, rounded corners, align=center, minimum height=8mm, minimum width=18mm, font=\small},
    gate/.style={draw, diamond, aspect=2, align=center, inner xsep=1mm, font=\small},
    flow/.style={-{Latex[length=2mm]}, thick}
  ]
  \node[stage] (plain) {Plaintext};
  \node[stage, right=of plain] (packet) {UTF-8\\ + AEAD packet};
  \node[stage, right=of packet] (split) {Bootstrap / body\\ segmentation};
  \node[stage, right=of split] (encode) {Candidate policy\\ + quantization\\ + interval narrowing};
  \node[stage, right=of encode] (cover) {Cover prefix};
  \node[stage, right=of cover] (tail) {Optional\\ natural tail};

  \node[stage, below=14mm of plain] (stego) {Received text};
  \node[stage, right=of stego] (tokenize) {Tokenize\\ under prompt};
  \node[stage, right=of tokenize] (header) {Interval inversion\\ (bootstrap)};
  \node[gate, right=of header] (check) {Header auth\\ + config\\ check};
  \node[stage, right=of check] (body) {Interval inversion\\ (body)};
  \node[gate, right=of body] (auth) {Packet auth};
  \node[stage, right=of auth] (recover) {Recovered\\ plaintext};

  \draw[flow] (plain) -- (packet);
  \draw[flow] (packet) -- (split);
  \draw[flow] (split) -- (encode);
  \draw[flow] (encode) -- (cover);
  \draw[flow] (cover) -- (tail);

  \draw[flow] (stego) -- (tokenize);
  \draw[flow] (tokenize) -- (header);
  \draw[flow] (header) -- (check);
  \draw[flow] (check) -- node[above, font=\small] {match} (body);
  \draw[flow] (body) -- (auth);
  \draw[flow] (auth) -- node[above, font=\small] {valid} (recover);

  \draw[flow] (cover.south) -- ++(0,-3mm) -| (stego.north);
  \node[font=\small, below=1mm of check] {fail closed on mismatch};
  \node[font=\small, below=1mm of auth] {fail closed on integrity failure};
\end{tikzpicture}
\caption{Ghostext end-to-end pipeline. The packet-carrying prefix is deterministic under matched configuration; optional tail does not carry payload.}
\Description{A two-path flow chart showing encode from plaintext to packet to token embedding, and decode from cover text to token inversion to plaintext, with configuration checks and fail-closed gates.}
\label{fig:pipeline}
\end{figure*}

Ghostext combines a cryptographic packet layer and an LLM token-selection layer (Figure~\ref{fig:pipeline}). The first protects message confidentiality and integrity. The second provides reversible embedding into generated cover text.

\subsection{Deterministic Synchronization}

Synchronization is a protocol invariant. Ghostext commits runtime settings, backend metadata, and prompt hash into a configuration fingerprint embedded in an authenticated internal header. Decoding proceeds only when this fingerprint matches local runtime state.

\subsection{Two-Stage Embedding Lifecycle}

Embedding is split into bootstrap and body stages. The bootstrap stage carries enough metadata for Bob to authenticate header information and determine expected body length before body decoding. This supports early rejection on mismatch and cleaner failure diagnosis.

\subsection{Operational Encode and Decode Semantics}

Alice starts with plaintext, passphrase, and shared prompt. Plaintext bytes are wrapped into an authenticated packet, then split into bootstrap and body segments. Each segment is mapped to token choices through deterministic candidate selection, quantization, and interval narrowing. Bob tokenizes the received text under the same prompt and replays the same deterministic distributions. Bootstrap bytes are reconstructed first, then header authentication and fingerprint checks are applied before body decoding. Plaintext is released only after full packet authentication.

Retries are enabled only when packet salt or nonce can be refreshed. If both are fixed, automatic retry is disabled by design. Low-entropy retry triggering uses a rolling entropy window:
\begin{equation}
\frac{1}{w}\sum_{j=t-w+1}^{t} H_j < \tau,
\end{equation}
where $H_j$ is candidate entropy at step $j$. In the current implementation defaults, $w=32$ and $\tau=0.1$ bits. These retry parameters are sender-side controls: failed attempts are discarded before transmission, Bob only receives the final successful cover, and decode replay never depends on hidden retry count $r$. When both salt and nonce are fixed, $r>1$ is disallowed by construction. This isolates correctness from retry count, but it does not hide retry-induced latency or energy variation from a traffic observer.

\subsection{Natural Tail Handling}

After packet resolution, the encoder may append a short natural tail. Tail tokens do not carry payload and are ignored by the decoder after packet recovery. In this version, tail generation reuses the same constrained candidate mechanism as the payload-carrying prefix, so its role is limited to output completion rather than a separate distribution-matching defense.

\subsection{Fail-Closed Principle and Failure Classes}

Mismatch, integrity failure, interval collapse, unstable tokenization paths, and token-budget exhaustion all trigger explicit failure. The decoder never emits partial plaintext after authentication failure.

Ghostext exposes a class-labeled failure taxonomy rather than a generic exception stream: authentication failures, configuration mismatch, synchronization mismatch, unstable-tokenization exhaustion, low-entropy retry exhaustion, and token-budget exhaustion. This makes deployment debugging and later evaluation analysis auditable.
