\section{Protocol}
\label{sec:protocol-details}

Ghostext combines a cryptographic packet layer and an LLM token-selection layer. The first protects confidentiality and integrity; the second provides reversible embedding into generated cover text.

\subsection{Operational Semantics}

Alice takes plaintext, passphrase, and shared prompt. Plaintext is wrapped into an authenticated packet, split into \emph{bootstrap} and \emph{body} segments, and mapped to token choices through deterministic candidate selection, quantization, and interval narrowing. Bob tokenizes the received text under the same prompt, replays the same distributions, reconstructs the bootstrap segment first, checks the header, and then decodes the body. Plaintext is released only after full packet authentication. After packet resolution the encoder may append a short natural tail that carries no payload and is ignored by the decoder.

Synchronization is a protocol invariant: sender and receiver must share the same prompt and decoding policy so that per-step distributions can be replayed deterministically. The decoder aborts on authentication mismatch, synchronization mismatch, unstable tokenization, or token-budget exhaustion, and never emits partial plaintext after authentication failure.

\subsection{Authenticated Packet Layer}

The packet format is
\begin{equation}
\begin{aligned}
\texttt{salt} \parallel \texttt{header\_nonce} \parallel \texttt{sealed\_header} \\
\parallel\ \texttt{body\_nonce} \parallel \texttt{body\_ciphertext}.
\end{aligned}
\end{equation}
The internal header stores protocol version, crypto IDs, and body length. The implementation uses scrypt for key derivation, HKDF-SHA256 for key separation, and ChaCha20-Poly1305 for authenticated encryption. Under standard AEAD assumptions and unknown passphrase, packet bytes are intended to be computationally indistinguishable from random given fixed field lengths; the arithmetic-coding layer is thus driven by a bitstream that is secret-independent at the byte level.

\subsection{Candidate Policy and Quantization}

At step $t$, raw logits define base distribution $P_t$ over vocabulary $\mathcal{V}$. Ghostext forms candidate set $C_t$ via deterministic top-$p$/max-$k$ truncation and renormalizes to $\widetilde{P}_t$. If $|C_t|<2$ or step entropy is below threshold $h_{\min}$, no payload bit is consumed. Retokenization-stability filtering then removes candidates that fail render/re-tokenize consistency.

Let $N_t=|C_t|$ and total frequency budget $F_{\mathrm{tot}}$. Each candidate $v\in C_t$ receives $f_t(v)=1+\lfloor \widetilde{P}_t(v)(F_{\mathrm{tot}}-N_t)\rfloor$, with leftover units distributed by fractional remainder and token-id tie-break; $Q_t(v)=f_t(v)/F_{\mathrm{tot}}$. Writing $\mathrm{cdf}^-_t(v)$ and $\mathrm{cdf}^+_t(v)$ for the lower and upper cumulative \emph{integer} frequencies of $v$, selecting token $v$ updates
\begin{align}
L_{t+1}&=L_t+\left\lfloor(H_t-L_t)\,\mathrm{cdf}^-_t(v)/F_{\mathrm{tot}}\right\rfloor,\\
H_{t+1}&=L_t+\left\lfloor(H_t-L_t)\,\mathrm{cdf}^+_t(v)/F_{\mathrm{tot}}\right\rfloor.
\end{align}
A segment resolves when $H_t-L_t=1$. Implementation defaults are $F_{\mathrm{tot}}=65536$ and $h_{\min}=1.0$ bit; the released baseline uses $F_{\mathrm{tot}}=4096$ and $h_{\min}=0.0$.

\subsection{Finite-Message Interval Coding}

Ghostext uses a finite-message integer interval codec at the segment level. For a segment $s$ of $n$ bytes, the encoder interprets the whole segment as a target integer $z=\mathrm{Int}(s)\in[0,2^{8n})$ and initializes $[L_0,H_0)=[0,2^{8n})$. At each payload-bearing step, the current quantized distribution partitions $[L_t,H_t)$ into candidate-specific subintervals. The encoder emits the unique token whose subinterval contains $z$; the decoder observes that token and mirrors the same interval update. Once the interval width becomes $1$, the segment is uniquely determined. This design stays fully integer based but avoids the extra renormalization machinery of a streaming range coder.

Algorithm~\ref{alg:segment-ac} makes this inner loop explicit. To keep the presentation short, it takes the quantized distributions $Q_t$ as already prepared inputs; deterministic candidate truncation, retokenization filtering, retry logic, and the post-packet natural tail are omitted here.

\begin{algorithm}[t]
\caption{Segment Arithmetic Coding (Simplified)}
\label{alg:segment-ac}
\begin{algorithmic}[1]
\REQUIRE segment bytes $s$, quantized distributions $\{Q_t\}_{t\ge 0}$
\ENSURE payload-bearing token sequence $y$
\STATE $z \leftarrow \mathrm{Int}(s)$
\STATE $L \leftarrow 0$; $H \leftarrow 2^{8|s|}$; $y \leftarrow [\ ]$
\FOR{$t=0,1,2,\dots$}
  \IF{$H-L=1$}
    \STATE \textbf{break}
  \ENDIF
  \STATE $Q \leftarrow Q_t$
  \IF{$Q$ forbids encoding}
    \STATE append $\mathrm{top}(Q)$ to $y$
    \STATE \textbf{continue}
  \ENDIF
  \FORALL{$v \in Q$}
    \STATE $L_v \leftarrow L + \lfloor (H-L)\,\mathrm{cdf}^-_Q(v)/F_{\mathrm{tot}} \rfloor$
    \STATE $H_v \leftarrow L + \lfloor (H-L)\,\mathrm{cdf}^+_Q(v)/F_{\mathrm{tot}} \rfloor$
    \IF{$L_v \le z < H_v$}
      \STATE append $v$ to $y$
      \STATE $L \leftarrow L_v$; $H \leftarrow H_v$
      \STATE \textbf{break}
    \ENDIF
  \ENDFOR
\ENDFOR
\RETURN $y$
\end{algorithmic}
\end{algorithm}

The decoder is the exact mirror image. For each observed payload-bearing token, it finds the token's index in the same quantized distribution $Q_t$, shrinks $[L_t,H_t)$ to that token's subinterval, and stops when $H_t-L_t=1$. The remaining integer point is then converted back to the unique $n$-byte segment. Deterministic no-payload steps must also match: when encoding is disabled, the receiver expects the top candidate and leaves the interval unchanged.

\subsection{Reference Pseudocode}
\label{sec:protocol-pseudocode}

Algorithm~\ref{alg:ghostext-encode} and Algorithm~\ref{alg:ghostext-decode} show the outer protocol-level data flow: \emph{packet $\rightarrow$ bitstream $\rightarrow$ per-token arithmetic-coding selection}. Algorithm~\ref{alg:segment-ac} makes the inner segment-level arithmetic step explicit.

\begin{algorithm}[t]
\caption{Ghostext Encode (Simplified)}
\label{alg:ghostext-encode}
\begin{algorithmic}[1]
\REQUIRE plaintext $m$, passphrase $pw$, prompt $\pi$
\ENSURE stego text $x$
\STATE $\mathrm{LLM.init}(\pi)$
\STATE $stream \leftarrow \mathrm{Packet}(m, pw)$
\STATE $AC \leftarrow \mathrm{ACEncoder.init}(stream)$
\WHILE{$\NOT \mathrm{ACEncoder.finished}(AC)$}
  \STATE $dist \leftarrow \mathrm{LLM.next\_token}()$
  \STATE $tok \leftarrow \mathrm{ACEncoder.select}(AC, dist)$
  \STATE $\mathrm{LLM.context.push}(tok)$
\ENDWHILE
\STATE \textit{// optional natural tail, no payload bits}
\RETURN $\mathrm{LLM.outputs}()$
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[t]
\caption{Ghostext Decode (Simplified)}
\label{alg:ghostext-decode}
\begin{algorithmic}[1]
\REQUIRE stego text $x$, passphrase $pw$, prompt $\pi$
\ENSURE plaintext $m$
\STATE $\mathrm{LLM.init}(\pi)$
\STATE $AC \leftarrow \mathrm{ACDecoder.init}(pw)$
\FORALL{$tok \in x$}
  \STATE $dist \leftarrow \mathrm{LLM.next\_token}()$
  \STATE $\mathrm{ACDecoder.update}(AC, tok, dist)$
  \STATE $\mathrm{LLM.context.push}(tok)$
\ENDFOR
\RETURN $\mathrm{ACDecoder.decode}(AC)$
\end{algorithmic}
\end{algorithm}
