\section{Evaluation}
\subsection{Evaluation Questions}
We evaluate three questions:
\begin{itemize}
\item Q1: Does Ghostext recover payloads under matched runtime configuration?
\item Q2: Does Ghostext fail closed under mismatch or mutation?
\item Q3: What practical overhead does Ghostext incur?
\end{itemize}

\subsection{Setup}
We use two backends:
\begin{itemize}
\item \textbf{Toy backend} for deterministic protocol-regression checks.
\item \textbf{Real backend} (`llama.cpp` + local Qwen3.5-2B GGUF) for practical execution behavior.
\end{itemize}
The evaluation scripts are rerunnable and emit structured JSON + markdown tables.

\subsection{Results}
\textbf{Toy backend baseline.}
Across four test cases, matched-configuration round-trip success is 4/4 (100\%), and fail-closed mismatch tests (wrong seed, wrong prompt, wrong passphrase, mutated text) fail as expected 4/4 (100\%).
\textbf{Real backend results.}
On two short real-model cases (one Chinese, one English), matched-configuration round-trip success is 2/2 (100\%). Mean embedding efficiency is 2.269 bits/token, and mean encode throughput is 13.73 tokens/s on the current CPU-only setup. A wrong-prompt sanity check fails closed with \texttt{SynchronizationError}.

\begin{table}[t]
\caption{Toy backend baseline (protocol-regression).}
\label{tab:toy-baseline}
\centering
\begin{tabular}{lrrrr}
\toprule
Case & Success & Packet Bytes & Total Tok & Bits/Tok \\
\midrule
zh\_short & Y & 118 & 1190 & 0.793 \\
en\_short & Y & 122 & 2523 & 0.387 \\
zh\_medium & Y & 157 & 1763 & 0.712 \\
en\_medium & Y & 154 & 3104 & 0.397 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[t]
\caption{Real backend results (\texttt{llama.cpp} + Qwen3.5-2B GGUF).}
\label{tab:real-backend}
\centering
\begin{tabular}{lrrrr}
\toprule
Case & Success & Packet Bytes & Total Tok & Bits/Tok \\
\midrule
zh\_real\_short & Y & 115 & 458 & 2.009 \\
en\_real\_short & Y & 117 & 370 & 2.530 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Artifacts.}
Primary outputs are exported to \texttt{results/minimal\_eval\_results.json}, \texttt{results/real\_backend\_eval\_results.json}, and \texttt{results/consolidated\_eval\_tables.md}.

\subsection{Interpretation Scope}
Results support recoverability and fail-closed claims within the stated passive-observer threat model and strict synchronization assumptions. These experiments do not establish detector resistance, active-channel robustness, or cross-model portability guarantees.
