\section{Implementation Snapshot (Evidence-Backed)}

\subsection{Codebase Modules}

Ghostext is organized as a small, explicit module set under \texttt{../Ghostext/src/ghostext}.

The cryptographic packet path is centered in \texttt{crypto.py} and \texttt{packet.py}. Runtime protocol structures and fingerprint logic are defined in \texttt{config.py}. Candidate construction and stability checks are in \texttt{candidate\_policy.py}. Deterministic integer quantization is in \texttt{quantization.py}. Interval encoder/decoder primitives are in \texttt{codec.py}. End-to-end orchestration lives in \texttt{encoder.py}, \texttt{decoder.py}, and \texttt{pipeline.py}. Backend abstraction is in \texttt{model\_backend.py}, with real llama.cpp support in \texttt{llama\_cpp\_backend.py}.

\subsection{Backend Paths and Default Runtime}

The CLI supports two backend paths.

The default path is a real local llama.cpp backend using GGUF models. Current defaults point to Qwen3.5-2B GGUF and include fixed seed, context size, batch size, top-$p$, candidate cap, and total frequency.

The second path is a deterministic toy character backend intended for protocol and regression tests. It provides fast, deterministic round-trip checks in both English and Chinese contexts.

\subsection{Model Asset and Prompt Template Handling}

Model-path resolution follows a deterministic fallback chain: explicit CLI path, environment variable path, local cache, then optional automatic download of the default model. Prompt template selection is model-family aware (for example, Qwen3 vs. Qwen3.5 variants). Template identity is included in tokenizer-hash derivation.

As a consequence, template drift changes backend metadata and therefore changes packet fingerprint validation behavior.

\subsection{Encoder Operational Safeguards}

The encoder includes several guard mechanisms to avoid silent failure modes.

It enforces bounded token budgets for header and body segments.

It tracks interval progress and raises a stall error if resolved bits stop increasing for too many steps.

It monitors rolling entropy and can trigger controlled retries with fresh packet randomness when low-entropy regimes persist.

It can enforce retokenization stability and fail closed if no stable candidate path exists.

\subsection{Decoder Integrity and Synchronization Checks}

The decoder first reconstructs the bootstrap segment, decrypts and authenticates internal header, checks fingerprint match, then decodes the body with exact expected length. Observed tokens that do not belong to the predicted candidate set trigger synchronization errors. Any authentication failure aborts output.

This ordering ensures that plaintext is never returned before integrity and synchronization checks are satisfied.

\subsection{Test Evidence Coverage}

Current tests in \texttt{../Ghostext/tests} provide direct evidence for the draft's reliability claims.

They cover crypto round-trip behavior and mismatch failures, deterministic quantization, codec invertibility in toy settings, failure handling under wrong prompt/seed or text mutation, retokenization-stability guard behavior, round-trip checks in English and Chinese toy modes, and optional real-model smoke integration when environment support exists.

The test suite is intentionally stronger on correctness and fail-closed behavior than on large-scale detectability claims. This is aligned with current project phase and claim discipline.
