\section{Evaluation Plan Under Experiment Pause}

The experiment pause is currently active, so this section defines what will be measured and reported after pause lift. No new numeric claims are made here.

\subsection{Research Questions}

The first question is \textbf{recoverability}: under synchronized configuration, how often does Bob recover exact plaintext, and what failure modes appear when decode fails.

The second question is \textbf{operational cost}: what latency, throughput, and token overhead are required at different message lengths and prompt families.

The third question is \textbf{embedding utilization}: how many payload bits are carried per packet token and per total generated token.

The fourth question is \textbf{distribution-facing security indicators}: how close stego outputs remain to baseline model outputs under fixed prompts and generation constraints.

The fifth question, marked preliminary for now, is \textbf{detector-facing behavior}: how existing steganalysis models and LLM-based surrogates behave as payload pressure changes.

\subsection{Evaluation Matrix (Planned)}

After pause lift, we plan to evaluate across a matrix of prompt styles, message lengths, and language settings (at least English and Chinese). Each condition will run with fixed seed policies and logged full configuration snapshots.

Runtime measurements will include end-to-end encode and decode latency, packet token counts, total token counts, and derived throughput metrics.

Recoverability reports will include both aggregate success rate and breakdown by failure class, using Ghostext's explicit error categories.

\subsection{Distribution and Detection Measurements (Planned)}

For distribution-facing analysis, we will follow the NLS-style framing~\cite{ziegler2019neural}: compare generated stego outputs against baseline model outputs under matched prompt families and report statistical divergence indicators.

For controlled tradeoff analysis, we will follow OD-Stega-style reporting logic~\cite{huang2026odstega} where applicable, while clearly marking that Ghostext currently does not implement OD adjustment and therefore should not be interpreted as reproducing OD gains.

For detector-facing analysis, we plan to run representative steganalysis baselines and an LLM-based evaluator as a human-like proxy, with strict labeling of this block as preliminary until replication quality is confirmed.

\subsection{Reproducibility Requirements for Every Reported Number}

Each reported number should include: model/version identity, backend identity, prompt policy, passphrase-handling policy (without revealing secrets), seed policy, candidate and codec settings, hardware context, and command/script references.

No table or figure should be included without recoverable raw artifacts.

\subsection{Pause-Aware Claim Boundary}

Until this plan is executed, this manuscript keeps all detector-resistance and active-edit robustness statements at preliminary status. Current evidence supports protocol correctness and fail-closed behavior claims, not broad empirical security claims.
