\section{Related Work}

NLS~\cite{ziegler2019neural} established arithmetic-coding neural steganography as a practical baseline. Later work explored adaptive and near-imperceptible variants~\cite{shen2020near,dai2019towards} and stronger formal constructions~\cite{zhang2021provably,ding2023discop,dewitt2024perfect}.

OD-Stega~\cite{huang2026odstega} is most directly related to Ghostext in terms of constrained-distribution perspective and tokenization mismatch emphasis.

Foundational information-theoretic and provable-security frameworks~\cite{cachin1998information,hopper2002provably} clarify what a complete steganographic security claim requires.

Ghostext is positioned as a systems-security implementation contribution: deterministic protocol behavior, synchronization binding, explicit failure semantics, and measurable approximation decomposition in an end-to-end codebase.

\subsection{Method Lineage and Security-Claim Styles}

The modern language-steganography line can be read along two axes. One axis is embedding mechanism, where arithmetic-coding-style approaches dominate practical neural systems~\cite{ziegler2019neural,shen2020near}. The second axis is claim style: some works primarily report empirical imperceptibility and utility trends, while others aim for formal indistinguishability guarantees under explicit assumptions~\cite{zhang2021provably,ding2023discop,dewitt2024perfect}.

Ghostext sits closer to the engineering side of this map. It keeps the arithmetic-coding family mechanism, but focuses on deterministic replay, fail-closed runtime semantics, and configuration binding under real implementation constraints. This is a narrower contribution than a new steganographic primitive, and the paper intentionally describes it in that scope.

\subsection{Practical Friction Points in Prior Systems}

Earlier neural approaches generally assume that sender and receiver can replay equivalent model distributions. In deployed systems, this assumption is stressed by tokenizer behavior, backend version drift, and finite-precision codec choices. OD-Stega explicitly discusses tokenizer mismatch risks~\cite{huang2026odstega}, which directly motivates Ghostext's retokenization-stability filtering and explicit mismatch checks.

Another practical gap is failure semantics. Many prior papers report aggregate performance but provide less structured runtime failure taxonomy for deployment troubleshooting. Ghostext emphasizes class-labeled failures because operational debugging and security interpretation often depend on distinguishing integrity failure, configuration mismatch, synchronization drift, and low-entropy stalls.

\subsection{Relation to Formal Frameworks}

Cachin's information-theoretic model~\cite{cachin1998information} and Hopper et al.'s provable framework~\cite{hopper2002provably} remain the conceptual baseline for strong security claims. Recent generative-text works with formal guarantees~\cite{zhang2021provably,ding2023discop,dewitt2024perfect} move closer to these standards under specific model-access assumptions.

Ghostext does not claim to replace those frameworks. Instead, it contributes implementation-level decomposition terms and an auditable evaluation blueprint intended to bridge engineering practice and stronger future claims. The design choice is to make approximation sources observable first, then upgrade claims only after corresponding measurements are available.

\subsection{Comparison of Contribution Focus}

\begin{table}[t]
\caption{Qualitative positioning of representative text-steganography lines (based on published descriptions).}
\label{tab:rw-positioning}
\begin{tabular}{p{0.24\linewidth}p{0.33\linewidth}p{0.36\linewidth}}
\toprule
Work line & Primary focus & Typical evidence emphasis \\
\midrule
NLS / adaptive arithmetic coding~\cite{ziegler2019neural,shen2020near,dai2019towards} & Practical neural embedding with distribution-guided token choice & Imperceptibility/quality and embedding performance trends \\
Provable generative constructions~\cite{zhang2021provably,ding2023discop,dewitt2024perfect} & Formal security guarantees under explicit assumptions & Theoretical guarantees with supporting experiments \\
OD-Stega~\cite{huang2026odstega} & Distribution optimization with explicit tokenization concerns & Empirical evaluation plus mechanism refinements \\
Ghostext (this work) & Deterministic protocol engineering, fail-closed semantics, reproducible measurement blueprint & Implementation-backed behavior, approximation decomposition, and post-pause experiment protocol \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Scope-Constrained Novelty Statement}

Given this landscape, Ghostext claims novelty at the systems-integration level: combining authenticated packet framing, runtime configuration binding, retokenization-aware candidate control, and explicit failure observability in one deterministic pipeline. Whether this combination yields significant detector-facing gains remains an empirical question and is explicitly deferred to post-pause evaluation.
