\section{Limitations and Conclusion}

\subsection{Limitations}

Ghostext currently targets passive-text observation and does not yet provide full empirical detector-resistance evidence.

Real-model evidence remains narrower than toy-backend protocol coverage, and the current real-backend sample is only a pilot 18-trial template-known baseline.

Cross-family model generalization is not yet established.

The current paper provides implementation-aligned bounds, not a full end-to-end indistinguishability proof.

The reported $2.478$ bits/token figure comes from an ungated baseline with $h_{\min}=0.0$ and should not be interpreted as a recommended deployment point.

The diagnostic $\widehat{B}_{\mathrm{TV}}$ is not yet calibrated against detector scores and should currently be read only as an implementation-side audit signal.

Deterministic replay is evidenced only within a pinned local environment; cross-hardware determinism is not yet established.

Active text modification in transit is out of scope in this revision.

Only an initial same-backend NLS-style comparison slice is included. A historical reproduction of official NLS/OD-Stega settings, larger-sample aligned baseline tables, and detector-side comparison remain pending before stronger positioning claims.

The released summaries still need two reproducibility upgrades: adding the exact llama.cpp commit SHA alongside the now-surfaced Ghostext commit and backend metadata, and surfacing the canonical upstream provenance behind the current third-party GGUF label.

\subsection{Evidence Upgrade Criteria}

To avoid overclaiming during later revisions, we define explicit promotion rules from design-time statements to evidence-backed claims.

First, any claim about recoverability must be supported by condition-stratified success rates and failure-class histograms, not only aggregate success numbers. Second, any claim about practical efficiency must include both packet-token and end-to-end transmission-token metrics with latency distributions. Third, any claim touching undetectability must include detector-facing and traffic-side results, together with approximation-term diagnostics, under clearly specified threat regimes. In particular, any argument that cites $\widehat{B}_{\mathrm{TV}}$ in a detector-facing context must calibrate it against detector outputs rather than treating it as self-validating.

If a statement cannot be tied to a released artifact entry (raw logs, aggregation scripts, and commit hashes), it should remain phrased as an open item or engineering intuition. This rule keeps narrative pressure from outrunning evidence.

\subsection{Open Technical Questions}

Several technical questions remain central for the next iteration.

How strong is the empirical coupling between approximation diagnostics (for example, large $\alpha_t$ or $\beta_t$ regions) and detector performance under sample accumulation?

How should retry policy be tuned when recoverability improves but traffic-side distinguishability worsens?

How stable are protocol outcomes across model-family changes where tokenization behavior and entropy profiles differ substantially?

Which operating envelope provides the best conservative tradeoff among decode success, payload efficiency, and side-channel footprint?

These are empirical questions. The current draft intentionally does not answer them beyond defining measurement pathways.

\subsection{Submission-Readiness Exit Conditions}

Before claim upgrades for a conference submission, three exit conditions should be satisfied.

(1) Main evaluation blocks from the staged protocol are complete with released artifacts.

(2) Failure and negative-result reporting is as complete as positive-result reporting.

(3) Claim language in each section is synchronized to measured evidence, with unresolved items explicitly downgraded to limitations or open items.

These conditions are process constraints, but they are also security-relevant: they reduce the risk that operationally fragile behavior is hidden by selective reporting.

\subsection{Conclusion}

Ghostext contributes a deterministic, fail-closed, implementation-auditable LLM steganography protocol with authenticated packetization, synchronization binding, and explicit approximation analysis.

This revision aligns title, threat model, baseline description, and approximation analysis more closely with the evidence that is actually released in the artifact bundle, treats the 18-trial real-backend results explicitly as a pilot operational floor rather than a completed security evaluation, and adds a first same-backend NLS-style comparison slice to separate payload normalization effects from broader detector claims.

The next milestone is to complete the remaining detector, traffic-side, and approximation-instrumentation stages with the same artifact discipline used for the baseline results.
